\chapter{Conclusion and future work} \label{conclusionandfuturework}

\section{Conclusion}

Most core functionalities have been implemented for Skylab including Submissions, Peer Evaluations, Feedback. However, as pointed in previous discussions as well, issues in security, usability and system design do exist as well and those issues will be addressed in the the coming semester. Besides, more features are expected of Skylab as well to make it serve Orbital program better such as registration of interest, mailer as reminders for deadlines and logging of user activities.

\section{Future work}

A proposed set of major features to be completed in the future for Skylab:

\begin{itemize}
  \item Questions/template system(involving migration of current data): currently \textit{Feedback} is utilizing the \textit{SurveyTemplate} and \textit{Question} system but \textit{Peer Evaluation} and \textit{Submission} are still not. With migration to \textit{Questions} system we can further improve the system by adding more extensibility.
  \item Public view of projects \& teams \& students: listing of previous projects as evidence of work from alumni of Orbital program can also help to attract more freshmen joining.
  \item Registration and post Orbital feedback: As part of Orbital program, registration of interest and post Orbital feedback should be captured in Skylab as well.
  \item Implementation of cohort: Orbital is held every year and certainly Skylab is expected to take cohort into consideration and allow historical records to be captured in the database.
  \item Implementation of more mailer actions: we can explore power of emails by sending reminder emails to students when deadlines are approaching or even embed secure link for students to do submissions without login.
  \item Logging of user activities: by logging down activities carried out by different users, users can more easily figure out what has happened and get a better sense of the context of Skylab.
\end{itemize}

