\chapter{Conclusion and future work} \label{conclusionandfuturework}

\section{Conclusion}

Skylab is supposed to serve facilitators, advisers, mentors and students and potential students well by making experience in Orbital more pleasant. Through the whole process of Orbital program, Skylab has been playing a helpful role in registration, match making after registration, submissions of project log and README, peer evaluations for evaluated teams` submissions and feedback to peer evaluations. There are also work done on admin portal for overseeing Skylab and reminding users and public views to display past projects and staff in Orbital program.

The development process of Skylab is certainly agile and iterative. Many features are developed as prototype first and after discussion adjustments are made to have a better user interaction experience. Besides, as Skylab is continuously being used, some requirements and suggestions are made by users as well. Many challenges to system design rise in the process of changing and refining. Various compromises have to be made to due to deadlines or other important issues. During implementation of Skylab, copying with changes and deadlines is the most important skill. Designing a system with enough features, with enough good features, with enough good features and extensibility to add more good features is huge challenge and Skylab is trying to be a system with many good features and open to extensions in the future.

\section{Future work}

A proposed set of major features to be completed in the future for Skylab:

\begin{itemize}
  \item Questions/template system(involving migration of current data): currently \textit{Feedback} and \textit{Peer Evaluation} is utilizing the \textit{SurveyTemplate} and \textit{Question} system but \textit{Submission} are still not. With migration to \textit{Questions} system we can further improve the system by adding more extensibility.
  \item Implementation of more mailer actions: we can explore power of emails by sending reminder emails to students when deadlines are approaching or even embed secure link for students to submit submissions, peer evaluations and feedback without login.
  \item Logging of user activities: by logging down activities carried out by different users, users can more easily figure out what has happened and get a better sense of the context of Skylab.
  \item Acceptance testing needs cover more use cases in Skylab by different users.
\end{itemize}

